The Astropy Project

### 2017-11-13 main.tex
visualization

\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   An example of this is given in \figurename \ref{fig:convolution-example}.  In versions $<=1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.  As of version 2.0, the two methods are consistent and include a suite of consistency checks.

@@

The \package{visualization} package provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization. Two main types of transformations are normalization and stretching of image values.

Normalization transforms the images values to the [0:1] range using lower and upper limits where $x$ represents the values in the original image:

\begin{equation}
y = \frac{x - v_{vmin}}{v_{max} - v_{min}}
\end{equation}

Stretching transforms the image values in the [0:1] range to the [0:1] range using a linear or non-linear function:
\begin{equation}
z = f(y)
\end{equation}

Several classes are provided for determining intervals (e.g. using image percentiles) and for normalizing values in this interval to the [0:1] range.

\package{Matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object.  The \package{visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.

@@

One of the most common tasks by astronomers dealing with observational data is to make figures with images that include the correct coordinates and optionally with a coordinate grid. The challenge however is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image. The \package{visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates. World coordinates can be for example right ascension and declination, but can also include for example velocity, wavelength, frequency, time, and so on. The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems. In addition, it is possible to pass data with more than two dimensions and slice on-the-fly. Finally, it is possible to define non-rectangular frames, such as for example for Aitoff projections.

This subpackage differs from APLpy \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of Matplotlib \citep{matplotlib}, and makes it possible to make significantly more advanced visualizations. An example of a visualization made with \package{wcsaxes} is shown in Figure~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image. This also uses the image stretching functionality from Section~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).

\begin{figure}
\includegraphics[width=\textwidth]{cygnus_x_spitzer.pdf}
\caption{%
An example of figure made using the \package{visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X Spitzer Legacy survey \citep{cygnusx}.
\label{fig:wcsaxes}
}
\end{figure}

@@

The package also provides the a histogram function, which is a generalization
of \package{matplotlib}’s histogram function, to allow for more flexible
specification of histogram bins.  The function provides several methods of
automatically tuning the histogram bin size. It has a syntax identical to
\package{matplotlib}’s histogram function (with the exception of the bins
parameter), which allows specification of one of four different methods for
automatic bin selection.

@@

\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays. The \package{visualization} package provides a convenience function to create such a color image.  It also includes an associated set of classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{lsst_astropy}.
% Please cite the final SPIE paper here rather than the presentation slides at that conference.
% https://ui.adsabs.harvard.edu/#abs/2016SPIE.9913E..0GJ/abstract (I'm not sure how to edit the bib file on overleaf)

>>>>

\astropypkg implements `normalized convolution' \citep[e.g.,][]{Knutsson1993}, which is an image reconstruction technique in which missing data are ignored during the convolution and replaced with values interpolated using the kernel.   An example of this is given in \figurename~\ref{fig:convolution-example}.  In versions $<=1.3$, the direct convolution and Fast Fourier Transform (FFT) convolution approaches were not consistent, with FFT convolution implementing normalized convolution and direct convolution implementing a different approach.  As of version 2.0, the two methods are consistent and include a suite of consistency checks.

@@

\package{astropy.visualization} provides a framework for transforming values in images (and more generally any arrays), typically for the purpose of visualization. Two main types of transformations are normalization and stretching of image values.

Normalization transforms the images values to the range $[0,1]$ using lower and upper limits $(v_{\rm min}, v_{\rm max})$
\begin{equation}
y = \frac{x - v_{\rm min}}{v_{\rm max} - v_{\rm min}}
\end{equation}
where $x$ represents the values in the original image.

Stretching transforms the image values in the range $[0,1]$ again to the range $[0,1]$ using a linear or non-linear function
\begin{equation}
z = f(y) \quad .
\end{equation}

Several classes are provided for automatically determining intervals (e.g., using image percentiles) and for normalizing values in this interval to the $[0,1]$ range.

\package{matplotlib} allows a custom normalization and stretch to be used when displaying data by passing a normalization object. The \package{astropy.visualization} package also provides a normalization class that wraps the interval and stretching objects into a normalization object that \package{matplotlib} understands.

@@

Astronomers dealing with observational imaging commonly need to make figures with images that include the correct coordinates and optionally display a coordinate grid. The challenge, however, is that the conceptual coordinate axes (such as longitude/latitude) need not be lined up with the pixel axes of the image. The \package{astropy.visualization.wcsaxes} subpackage implements a generalized way of making figures from an image array and a world coordinate system (WCS) object that provides the transformation between pixel and `world' coordinates.

World coordinates can be, for example, right ascension and declination, but can also include, for example, velocity, wavelength, frequency, or time. The main features from this subpackage include the ability to control which axes to show which coordinate on (for example showing longitude ticks on the top and bottom axes and latitude on the left and right axes), controlling the spacing of the ticks either by specifying the positions to use or providing a tick spacing or an average number of ticks that should be present on each axis, setting the format for the tick labels to ones commonly used by astronomers, controlling the visibility of the grid/graticule, and overlaying ticks, labels, and/or grid lines from different coordinate systems. In addition, it is possible to pass data with more than two dimensions and slice on-the-fly. Finally, it is possible to define non-rectangular frames, such as, for example, Aitoff projections.

This subpackage differs from \package{APLpy} \citep{aplpy} in that the latter focuses on providing a very high-level interface to plotting that requires very few lines of code to get a good result, whereas WCSAxes defines an interface that is much closer to that of \package{matplotlib} \citep{matplotlib}. This enables significantly more advanced visualizations.

An example of a visualization made with \package{wcsaxes} is shown in \figurename~\ref{fig:wcsaxes} -- this example illustrates the ability to overlay multiple coordinate systems and customize which ticks/labels are shown on which axes around the image. This also uses the image stretching functionality from \sectionname~\ref{sec:stretch} to show the image in a square root stretch (automatically updating the tick positions in the colorbar).

\begin{figure}
\includegraphics[width=\textwidth]{cygnus_x_spitzer.pdf}
\caption{%
An example of figure made using the \package{astropy.visualization.wcsaxes} subpackage, using \textit{Spitzer}/IRAC 8.0$\mu$m data from the Cygnus-X \textit{Spitzer} Legacy survey \citep{cygnusx}.
\label{fig:wcsaxes}
}
\end{figure}

@@

\package{astropy.visualization} also provides a histogram function, which is a
generalization of \package{matplotlib}’s histogram function, to allow for more
flexible specification of histogram bins.  The function provides several methods
of automatically tuning the histogram bin size. It has a syntax identical to
\package{matplotlib}’s histogram function, with the exception of the \texttt{bins}
parameter, which allows specification of one of four different methods for
automatic bin selection: `blocks', `knuth', `scott', or `freedman'.

@@

\cite{Lupton2004} describe an ``optimal'' algorithm for producing red-green-blue (RGB) composite images from three separate high-dynamic range arrays. The \package{astropy.visualization} subpackage provides a convenience function to create such a color image.  It also includes an associated set of classes to provide alternate scalings.
This functionality was contributed by developers from the Large Synoptic Survey Telescope (LSST) and serves as an example of contribution to Astropy from a more traditional engineering organization \citep{Jennes2016}.
